Quantum Pseudo-Telepathy

### 2023-06-23 paper/main.tex
Tables shared eigenvectors

\usepackage[table]{xcolor}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{hhline}
\usepackage{bigdelim}

@@

\begin{proof}
  \label{proof:product}
  First, notice that \(X^{2} = Z^{2} = Y^{2} = I\), \(XZ = \ci{}Y\) and
  \(ZX = -\ci{}Y\) (i.e. \(X\) and \(Z\) anticommute), and, similarly,
  \(XY = \ci{}Z\) and \(YX = -\ci{}Z\). Using these properties, we can see
  that the product of every row (equiv. column) is the identity \(I\)
  (equiv. \(-I\)), regardless of the order of the three observables.
  That is, the three observables of every row and every column
  mutually commute (or, in other words, they are compatible).
  Consequently, for every row and every column, it is possible to find
  a basis of eigenvectors that are common to the three observables,
  meaning that they can be simultaneous
  diagonalized. Figure~\ref{fig:eigenv} shows these common
  eigenvectors. Let  \(M_{i, j}\) be the observables at each cell.
  Then, for every row \(i\) (equiv. column \(j\)), we have
  \begin{align}
    M_{i, 0} M_{i, 1} M_{i, 2}
    &= (P_{i} \Lambda_{i, 0} P_{i}^{-1}) (P_{i}\Lambda_{i, 1}P_{i}^{-1}) (P_{i}\Lambda_{i, 2}P_{i}^{-1})
      \nonumber \\
    &= P_{i}(\Lambda_{i, 0} \Lambda_{i, 1} \Lambda_{i, 2})P_{i}^{-1} \nonumber \\
    &= P_{i}\Lambda_{i}P_{i}^{-1},
  \end{align}
  where \(P_{i}\) is the matrix whose columns are the common
  eigenvectors and \(\Lambda_{i}\) is the matrix whose diagonal is
  formed by the products of the eigenvalues of the observables,
  associated with the same eigenvector. What this essentially means is
  that any measurement \(M_{i, j}\) yields one of the eigenvalues
  \(\lambda\) in the diagonal of \(\Lambda_{i, j}\) and collapses the
  state to a linear combination of one of the two shared eigenvectors
  \(\ket{\lambda}_{1}\) and \(\ket{\lambda}_{2}\) in the
  \(\lambda\)-eigenspace. Then, the second measurement will collapse
  the state to either \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\).
  Consequently, the third measurement will not change the state any
  further. Therefore, the product of the three outcomes will be the
  product of the eigenvalues associated with either
  \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\), which is one of the
  entries in the diagonal of \(\Lambda_{i}\). But, notice that
  \(P_{i}\Lambda_{i}P_{i}^{-1} = I\); thus, \(\Lambda_{i} = I\) and
  the only possible value for the product is \(1\) (equiv. \(-1\) for
  columns).
\end{proof}

>>>>

\usepackage[table]{xcolor}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{hhline}
\usepackage{bigdelim}
\usepackage{booktabs}

@@

\begin{proof}
  \label{proof:product}
  First, notice that \(X^{2} = Z^{2} = Y^{2} = I\), \(XZ = \ci{}Y\)
  and \(ZX = -\ci{}Y\) (i.e. \(X\) and \(Z\) anticommute), and,
  similarly, \(XY = \ci{}Z\) and \(YX = -\ci{}Z\). Using these
  properties, we can see that the product of every row (equiv. column)
  is the identity \(I\) (equiv. \(-I\)), regardless of the order of
  the three observables.  That is, the three observables of every row
  and every column mutually commute (or, in other words, they are
  compatible).  Consequently, for every row and every column, it is
  possible to find a basis of eigenvectors that are common to the
  three observables, meaning that they can be diagonalized
  simultaneously. Tables~\ref{tab:eigenv-rows} and \ref{tab:eigenv-cols} show
  these common eigenvectors. Let \(M_{i, j}\) be the observables at
  each cell.  Then, for every row \(i\) (equiv. column \(j\)), we have
  \begin{align}
    M_{i, 0} M_{i, 1} M_{i, 2}
    &= (P_{i} \Lambda_{i, 0} P_{i}^{-1}) (P_{i}\Lambda_{i, 1}P_{i}^{-1}) (P_{i}\Lambda_{i, 2}P_{i}^{-1})
      \nonumber \\
    &= P_{i}(\Lambda_{i, 0} \Lambda_{i, 1} \Lambda_{i, 2})P_{i}^{-1} \nonumber \\
    &= P_{i}\Lambda_{i}P_{i}^{-1},
  \end{align}
  where \(P_{i}\) is the matrix whose columns are the common
  eigenvectors and \(\Lambda_{i}\) is the matrix whose diagonal is
  formed by the products of the eigenvalues of the observables,
  associated with the same eigenvector. What this essentially means is
  that any measurement \(M_{i, j}\) yields one of the eigenvalues
  \(\lambda\) in the diagonal of \(\Lambda_{i, j}\) and projects the
  state onto the \(\lambda\)-eigenspace. That is, it collapses the
  state to a linear combination of the two shared eigenvectors
  \(\ket{\lambda}_{1}\) and \(\ket{\lambda}_{2}\) in the
  \(\lambda\)-eigenspace. Then, the second measurement will collapse
  the state to either \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\),
  eigenvectors common to the three observables.  Consequently, the
  third measurement will not change the state any further. Therefore,
  the product of the three outcomes will be the product of the
  eigenvalues associated with either \(\ket{\lambda}_{1}\) or
  \(\ket{\lambda}_{2}\), which is one of the entries in the diagonal
  of \(\Lambda_{i}\). But, notice that
  \(P_{i}\Lambda_{i}P_{i}^{-1} = I\); thus, \(\Lambda_{i} = I\) and
  the only possible value for the product is \(1\) (equivalently
  \(-1\) for columns). \qed
\end{proof}

\begin{table}[htbp]
  \centering
  \caption{Eigenvectors shared by the observables at each row of the quantum magic square.
    The eigenvectors were taken from~\ref{xxx}, adapting to the correct eigenvalues.}
  \label{tab:eigenv-rows}
  \begin{tabular}{c*{4}{>{\;\;}c}}
    \toprule
    & & Column 1 & Column 2 & Column 3 \\
    \midrule
    \multirow{2}{*}{Row 1} & \(+1\)
      & \ket{00}, \ket{10} & \ket{00}, \ket{01} & \ket{00}, \ket{11} \\
    & \(-1\)
      & \ket{01}, \ket{11} & \ket{10}, \ket{11} & \ket{01}, \ket{10} \\
    \midrule
    \multirow{4}{*}{Row 2} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\), \\ 
    & & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} 
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\)\phantom{,} 
                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\)\phantom{,} \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\), \\ 
    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\)\phantom{,} 
                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} 
                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} \\
    \midrule
    \multirow{4}{*}{Row 3} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\), \\ 
    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\), \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\), \\
    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\),
                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\),
                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\), \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{Eigenvectors shared by the observables at each column of the quantum magic square.
    The eigenvectors were taken from~\ref{xxx}, adapting to the correct eigenvalues.}
  \label{tab:eigenv-cols}
  \begin{tabular}{c*{4}{>{\;\;}c}}
    \toprule
    & & Row 1 & Row 2 & Row 3 \\
    \midrule
    \multirow{4}{*}{Column 1} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{10})\),
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{10})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10})\), \\
    & &  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{11})\)\phantom{,} \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{11})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{10})\), \\
    & & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\)\phantom{,} \\
    \midrule
    \multirow{4}{*}{Column 2} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{01})\),
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{01})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{01})\), \\
    & &  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{01})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} + \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} + \ket{11})\)\phantom{,} \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} + \ket{11})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{01})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{01})\), \\
    & & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} - \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} - \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} - \ket{11})\)\phantom{,} \\
    \midrule
        \multirow{4}{*}{Column 3} & \multirow{2}{*}{\(+1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{11})\),
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{11})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{10})\), \\
    & &  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{11})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{10})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{11})\)\phantom{,} \\[1.5mm]
    & \multirow{2}{*}{\(-1\)}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{10})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{11})\), 
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{11})\), \\
    & & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{10})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{10})\)\phantom{,}
      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{10})\)\phantom{,} \\
    \bottomrule
  \end{tabular}
\end{table}
